On the Minimum Core Mass for Giant Planet Formation at Wide Separations

### 2014-03-07 tex/PaperI/ms.tex
small Paper I edits

In the low mass regime, $M\pla < M_{\rm th}/\sqrt{3}$, the length scales order as $\RB< \RH<H\di$.  In this regime, many studies assume the atmosphere matches the disk conditions at $\RB$.  We use $\RH$ as the matching radius, i.e.\ outer boundary, in all regimes.  
\textbf{This choice reflects the fact that, even outside the Bondi radius, hydrostatic densities exceed the background density (see R06). Nevertheless, since the density contrast is modest outside $\RB$, these two boundary conditions give similar results.  We do not extend our models past $\RH$, where tidal forces dominate. }

@@

\subsection{Hydrodynamic Effects}\label{sec:hydro}
The neglect of hydrodynamical effects in our model is best discussed in terms of the thermal mass, $M_{\rm th}$, and the length scales introduced in \S\ref{sec:scales}.  In the low mass regime, $M\pla < M_{\rm th}/ \sqrt{3}$, where $\RB < \RH$, we assume that hydrostatic balance holds out to the outer boundary at $\RH$.   In this low mass regime, \citet[]{Orm13} calculated the flow patterns driven by stellar tides and disk headwinds.     On scales $\gtrsim \RB$ the flows no longer circulate the planet: they belong to the disk.  Nevertheless, the density structure outside $\RB$ remains spherically symmetric and hydrostatic.  Even if these flows do not destroy hydrostatic balance, they could affect the planet's cooling.  We expect such effects to be weak, as heat losses at greater depths dominate planetary cooling, but more study is needed.

>>>>

In the low mass regime, $M\pla < M_{\rm th}/\sqrt{3}$, the length scales order as $\RB< \RH<H\di$.  In this regime, many studies assume the atmosphere matches the disk conditions at $\RB$.  We use $\RH$ as the matching radius, i.e.\ outer boundary, in all regimes.  
%\textbf{This choice reflects the fact that, even outside the Bondi radius, hydrostatic densities exceed the background density (see R06). Nevertheless, since the density contrast is modest outside $\RB$, these two boundary conditions give similar results.  We do not extend our models past $\RH$, where tidal forces dominate. }

@@

\subsection{Hydrodynamic Effects}\label{sec:hydro}
The neglect of hydrodynamical effects in our model is best discussed in terms of the thermal mass, $M_{\rm th}$, and the length scales introduced in \S\ref{sec:scales}.  In the low mass regime, $M\pla < M_{\rm th}/ \sqrt{3}$, where $\RB < \RH$, we assume that hydrostatic balance holds out to the outer boundary at $\RH$.   In this low mass regime, \citet[]{Orm13} calculated the flow patterns driven by stellar tides and disk headwinds.     On scales $\gtrsim \RB$ the flows no longer circulate the planet: they belong to the disk. Even if these flows do not destroy hydrostatic balance, they could affect the planet's cooling.  We expect such effects to be weak, as heat losses at greater depths dominate planetary cooling, but more study is needed.

 %Nevertheless, the density structure outside $\RB$ remains spherically symmetric and hydrostatic.
